---
title: "Venture Capital Images"
output: html_notebook
---


**Key takeaways:**  

*  **Venture Capital Investment in Louisville has increased dramatically in the last two years.**
*  **Louisville is roughly average for per capita VC investment over the timeframe 2008-2019.**
*  **Louisville's VC scene is composed of a higher number of smaller deals than the average peer city.**
*  **Louisville receives a higher-than-average percent of VC dollars from in-state, but Louisville has a smaller-than-average percent of VC deals from in-state investors. In-state deals are larger than deals from out-of-state, on average.**

```{r setup}
library(tidyr)
library(readr)
library(dplyr)
library(stringr)
library(magrittr)
library(glptools)

library(broom)
library(purrr)

library(feather)
library(classInt)
library(scales)
library(ggplot2)
library(ggthemes)
library(ggrepel)

library(showtext)
showtext_auto()
setwd("../..")
font_add("Museo Sans 300", "MuseoSans_300.otf")
font_add("Museo Sans 300 Italic", "MuseoSans_300_Italic.otf")

```

```{r data}
for(c in unique(FIPS_df$city[FIPS_df$current == 1])){
  df <- readxl::read_xlsx("data/Investments by City.xlsx",
                          sheet = c, skip = 31, col_types = c("numeric", "numeric", "numeric"),
                          col_names = c("year", "capital", "deals"))
  
  df$city <- c
  
  capital_all <- assign_row_join(capital_all, df)

  
  df <- readxl::read_xlsx("data/Investments by City with Investor Screen.xlsx", 
                          sheet = c, skip = 31, col_types = c("numeric", "numeric", "numeric"),
                          col_names = c("year", "capital_instate", "deals_instate"))
  
  df$city <- c
  
  capital_in_state <- assign_row_join(capital_in_state, df)
}

FIPS_df <- FIPS_df %>% filter(FIPS %not_in% c(29189, 29510))

population_df_merged_2019 <- population_df_merged %>%
  filter(year == 2018) %>%
  mutate(year = 2019)

population_df_merged_all <- bind_rows(population_df_merged, population_df_merged_2019)

lou_population <- population_df_merged_all %>% 
  filter(FIPS == 21111) %>% 
  transmute(year, pop_lou = population)

MSA_pop <- glpdata:::population %>% select(FIPS, year, core_county_pct)
MSA_pop_18 <- MSA_pop %>% filter(year == 2017) %>% mutate(year = 2018)
MSA_pop_19 <- MSA_pop %>% filter(year == 2017) %>% mutate(year = 2019)
MSA_pop %<>% bind_rows(MSA_pop_18, MSA_pop_19)
MSA_pop %<>% 
  left_join(population_df_merged_all, by = c("FIPS", "year")) %>%
  mutate(MSA_pop = population * 100 / core_county_pct) %>%
  select(FIPS, year, MSA_pop)

MSA_lou_pop <- MSA_pop %>%
  filter(FIPS == 21111) %>%
  transmute(year, lou_MSA_pop = MSA_pop)

capital <- full_join(capital_all, capital_in_state, by = c("year", "city")) %>%
  rbind(c(2008, 0, 0, unname(as.list("Greensboro")), 0, 0))  %>%
  left_join(FIPS_df, by = "city") %>%
  left_join(population_df_merged_all, by = c("FIPS", "year")) %>%
  left_join(lou_population, by = "year") %>%
  left_join(MSA_pop, by = c("FIPS", "year")) %>%
  left_join(MSA_lou_pop, by = "year") %>%
  mutate_at(vars(capital, capital_instate, deals, deals_instate), replace_na, 0) %>%
  mutate(
    capital_outstate = capital - capital_instate,
    deals_outstate = deals - deals_instate) %>%
  transmute(
    FIPS, year, MSA_pop,
    capital = capital * 1000000,
    capital_outstate = capital_outstate * 1000000,
    
    capital_pp = capital / MSA_pop,
    capital_outstate_pp = capital_outstate / MSA_pop,
    
    deals, deals_outstate,
    
    deals_pp = deals / MSA_pop,
    deals_outstate_pp = deals_outstate / MSA_pop,
    deal_size = capital / deals) %>%
  COLA(capital:capital_outstate_pp, base_year = 2019, rpp = FALSE) %>%
  organize()
```

```{r graphs}
showtext_auto()

graph_df <- data.frame(
  variable = names(capital)[4:12],
  title = c("VC Investment", "Out-of-State VC Investment", 
            "VC Investment per capita", "Out-of-State VC Investment per capita",
            "VC Deals", "Out-of-State VC Deals",
            "VC Deals per million residents", "Out-of-State VC Deals per million residents",
            "VC Deal Size"),
  y_axis = c(rep("Dollars", 4), rep("Deals", 4), "Dollars"),
  axis_3 = c(9, 8, 15, 15, 17, 18, 18, 18, 18),
  axis_all = c(11, 11, 16, 17, 18, 18, 18, 18, 18),
  per_capita = c(F, F, T, T, F, F, T, T, F),
  single_year = c(F, F, F, F, T, T, T, T, F),
  stringsAsFactors = FALSE)
  
for(r in 1:nrow(graph_df)){
  g <- graph_df[r,]
  
  print(g$variable)
  
  if (g$y_axis == "Deals") {
    if (g$per_capita) {
      label_fxn <- comma_format(accuracy = 0.1, scale = 1000000)
      axis_fxn  <- comma_format(accuracy = 1, scale = 1000000)
    } else {
      label_fxn <- comma_format(accuracy = 0.1, scale = 1)
      axis_fxn  <- comma_format(accuracy = 1, scale = 1)
    }
  } else if (g$y_axis == "Dollars"){
    if (g$per_capita) {
      label_fxn <- dollar_format(accuracy = 0.1, scale = 1)
      axis_fxn  <- dollar_format(accuracy = 1, scale = 1)
    } else {
      label_fxn <- dollar_format(accuracy = 0.1, scale = .000001, suffix = "M")
      axis_fxn  <- dollar_format(accuracy = 1, scale = .000001, suffix = "M")
    }
  } else {
    label_fxn <- NULL
    axis_fxn  <- NULL
  }
  
  if (g$y_axis == "Dollars") subtitle <- "Adjusted for inflation" else subtitle <- ""
  
  if (g$single_year) {
    png("images/" %p% g$variable %p% "_ranking.png", 3000, 2400, res = 200)
    p <- ranking(capital, g$variable, 2018, plot_title = g$title %p% ", 2018",
                 y_title = g$y_axis, 
                 subtitle_text = subtitle, caption_text = "GLP analysis of PitchBook data",
                 alternate_text = g$axis_3:17, label_function = label_fxn, sigfig = 4)
    print(p)
    dev.off()
  } else {
    png("images/" %p% g$variable %p% "_ranking_3.png", 3000, 2400, res = 200)
    p <- ranking(capital, g$variable, 2017:2019, plot_title = g$title %p% ", 2017-2019 Average",
                 y_title = g$y_axis, 
                 subtitle_text = subtitle, caption_text = "GLP analysis of PitchBook data",
                 alternate_text = g$axis_3:17, label_function = label_fxn, sigfig = 4)
    print(p)
    dev.off()
  }
  
  png("images/" %p% g$variable %p% "_ranking_all.png", 3000, 2400, res = 200)
  p <- ranking(capital, g$variable, 2008:2019, plot_title = g$title %p% ", 2008-2019 Average", 
               y_title = g$y_axis, 
               subtitle_text = subtitle, caption_text = "GLP analysis of PitchBook data",
               alternate_text = g$axis_all:17, label_function = label_fxn, sigfig = 4)
  print(p)
  dev.off()
  
  png("images/" %p% g$variable %p% "_trendline.png", 3000, 2400, res = 200)
  p <- trend(capital, g$variable, plot_title = g$title, y_title = g$y_axis, 
             subtitle_text = subtitle, caption_text = "GLP analysis of PitchBook data",
             label_function = label_fxn,
             axis_function = axis_fxn)
  print(p)
  dev.off()
  
  png("images/" %p% g$variable %p% "_trendline_3yr.png", 3000, 2400, res = 200)
  p <- trend(capital, g$variable, plot_title = g$title, y_title = g$y_axis, 
             subtitle_text = subtitle, caption_text = "GLP analysis of PitchBook data",
             rollmean = 3,
             label_function = label_fxn,
             axis_function = axis_fxn)
  print(p)
  dev.off()
}
```

```{r capital_pop_relationship}
capital_avg_3yr <- capital %>%
  filter(year %in% 2017:2019) %>%
  group_by(FIPS) %>%
  summarise_at(vars(MSA_pop:deal_size), mean) %>%
  pull_peers_FIPS()

capital_avg <- capital %>%
  group_by(FIPS) %>%
  summarise_at(vars(MSA_pop:deal_size), mean) %>%
  pull_peers_FIPS()

png("images/investment_population_3yr.png", 3000, 2400, res = 200)
g <- ggplot(capital_avg_3yr, aes(x = MSA_pop, y = capital_pp, label = city)) +
  geom_point(size = 5) + 
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(labels = comma_format()) +
  scale_y_continuous(labels = dollar_format()) +
  geom_text_repel(size = 16, family = "Museo Sans 300")

g %<>% glptools:::tl_style(
  plot_title = "VC investment per capita and population, 2017-2019 Average",
  y_title = "Average VC investment per capita",
  x_title = "Average Population",
  caption_text = "",
  subtitle_text = "",
  cat_names = "")
print(g)
dev.off()


png("images/investment_population.png", 3000, 2400, res = 200)
g <- ggplot(capital_avg, aes(x = MSA_pop, y = capital_pp, label = city)) +
  geom_point(size = 5) + 
  geom_smooth(method = "lm", se = FALSE) +
  scale_x_continuous(labels = comma_format()) +
  scale_y_continuous(labels = dollar_format()) +
  geom_text_repel(size = 16, family = "Museo Sans 300")

g %<>% glptools:::tl_style(
  plot_title = "VC investment per capita and population, 2008-2019 Average",
  y_title = "Average VC investment per capita",
  x_title = "Average Population",
  caption_text = "",
  subtitle_text = "",
  cat_names = "")
print(g)
dev.off()
```

```{r outstate_percent}
capital %<>% mutate(ratio = capital_outstate / capital * 100)
capital_avg %<>% mutate(ratio = capital_outstate / capital * 100)
capital_avg_3yr %<>% mutate(ratio = capital_outstate / capital * 100)

png("images/outstate_ratio_3.png", 3000, 2400, res = 200)
p <- ranking(capital_avg_3yr, "ratio", 
             plot_title = "Percent of VC from Out-of-State, 2017-2019",
             subtitle_text = "Adjusted for inflation", 
             caption_text = "GLP analysis of PitchBook data")
print(p)
dev.off()

png("images/outstate_ratio_all.png", 3000, 2400, res = 200)
p <- ranking(capital_avg, "ratio", 
             plot_title = "Percent of VC from Out-of-State, 2008-2019",
             subtitle_text = "Adjusted for inflation", 
             caption_text = "GLP analysis of PitchBook data")
print(p)
dev.off()

png("images/outstate_ratio_trendline_3yr.png", 3000, 2400, res = 200)
p <- trend(capital, ratio, plot_title = "Percent of VC from Out-of-state", rollmean = 3,
           subtitle_text = "Adjusted for inflation", caption_text = "GLP analysis of PitchBook data")
print(p)
dev.off()

png("images/outstate_ratio_trendline_all.png", 3000, 2400, res = 200)
p <- trend(capital, ratio, plot_title = "Percent of VC from Out-of-state",
           subtitle_text = "Adjusted for inflation", caption_text = "GLP analysis of PitchBook data")
print(p)
dev.off()
```

